%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper]{moderncv}

% moderncv themes
					      % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[margin=0.75in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\newcommand{\responsibilities}[1]{#1}
\newcommand{\achievements}[1]{#1}

\usepackage{multicol}

% personal data
\InputIfFileExists{personalinfo.tex}{}{
\firstname{John}
\familyname{Smith Doe}
\mobile{(123) 456 7890}
\email{me@email.com}
}

\let\originalrecomputecvlengths\recomputecvlengths
\renewcommand*{\recomputecvlengths}{%
\originalrecomputecvlengths%
\setlength{\quotewidth}{0.9\textwidth}}

\nopagenumbers{}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-1.0cm}

\textcolor{color2}{I've spent a decade leading diverse software teams and building the critical systems that power our lives.}
% With a decade of experience building critical systems, I want to lead a diverse org of senior software engineers to build the systems that power our lives.

\vspace{-0.1cm} 
\section{Experience}

\cventry{Apr 2021 - Nov 2021}{Director of Engineering}{Streamlit}{San Francisco, CA}{}{
\responsibilities{
    Responsible for leading the Platform organization (15 people across 3 teams and 8 timezones). \\
    Responsible for aligning engineering goals, processes, and roadmaps across teams. \\
    Responsible for hiring and coaching senior engineering leaders and managers.
}
\achievements{\begin{itemize}
\item Grew engineering by 9 people with 90\% offer acceptance rate and 45\% URM candidates.
\item Increased ARR by >400\% by launching SaaS product in collaboration with Product and Sales.
\item Coached and promoted an individual contributor into becoming the manager of a team.
\end{itemize}}
}

\cventry{Sep 2020 - Jan 2021}{Engineering Manager}{Roblox}{San Francisco, CA}{}{
\responsibilities{
    Responsible for managing Microservices Platform team (5 people, including 4 Principal Engineers).}
\achievements{\begin{itemize}
\item Improved relationships and created first joint roadmap for Microservices and Orchestration teams.
% \item Stabilized long delayed service mesh project by diagnosing technical and organizational issues
% \item Finalist in company Hack Week for prototyping automatic coredump analysis tool.
\end{itemize}}
}

\cventry{Oct 2018 - Jun 2020}{Engineering Manager}{Twitter}{San Francisco, CA}{}{
\responsibilities{
    Responsible for managing Revenue SRE team (8 engineers, 4 SWE \& 4 SRE).}
\achievements{\begin{itemize}
\item Team won 2020 EPDR award ``Improving our Focus'' (top 5 engineering team in the company). 
% \item Improved weekly successful deploy rate of major services at Twitter by 2x by building automatic load testing tool.
\item Team pulse exceptionally high during COVID (94/100, +11 vs average for company).
\item Created new promo packet template to be rolled out Twitter-wide with Project Sol committee.
\item Hired 5 engineers onto the team, including 4 SWEs and 1 Senior Staff SWE.
\item Coached and successfully promoted 3 engineers on the team to Senior Engineer level.
% \item Built consensus on and standardized SRE org-wide interview screen questions.
\end{itemize}}
}

\cventry{May 2018 - July 2018}{Backend Engineer}{Brex}{San Francisco, CA}{}{
\responsibilities{Responsible for improving engineering at Brex.}
\achievements{\begin{itemize}
\item Reduced support load by 60\% by rewriting accounting integration to handle network failures.
\end{itemize}}
}

\cventry{Oct 2017 - Mar 2018}{Lead Engineer}{AlphaFlow}{San Francisco, CA}{}{
\responsibilities{Responsible for stabilizing the backend website and bringing process to the engineering team.}
\achievements{\begin{itemize}
% \item Introduced project planning and CI/CD practices to engineering team.
\item Enabled BI tools and reduced cash drag by leading migration from MongoDB to PostgreSQL.
% \item Improved engineering efficiency by building new Go architecture with static analysis tools.
\end{itemize}}
}


\cventry{May 2015 - Oct 2017}{Senior Performance Engineer}{MemSQL}{San Francisco, CA}{}{
\responsibilities{Responsible for the performance of a real time database in production environments.}
\achievements{\begin{itemize}
% \item Introduced post-mortems, the USE method, and flamegraphs to standardize the debugging process.
% \item Mentored a college intern on a C++ project and helped them write a viral blog post.
\item Released an in-database resource profiler with a team of 3 engineers.
\item Interviewed 85 candidates in engineering, support, sales, and product management.
% \item Created 8 week onboarding process for new support engineers.
\item Invited to 2017 Presidents Club (top 2 engineer in the company) for contributions to sales team.
\item Created a company incident response process unifying sales, engineering, support, and marketing.
\end{itemize}}
 }


\cventry{Jul 2013 - May 2015}{Member of Technical Staff}{Delphix}{San Francisco, CA}{}{
\responsibilities{
Contributed to the Zettabyte Filesystem (ZFS) kernel module. 
% \\ Responsible for developer productivity and devops. 
% \\ Responsible for product security and running the security team.
}
\achievements{\begin{itemize}
% \item Evangelized the ZFS team by talking at open source conferences and giving college tech talks.
\item \href{https://patents.justia.com/patent/10372329}{Patent US10372329} for extending ZFS to allow the live removal of devices from the storage pool.
\item Built ZFS block allocation strategy that defragmented on-line devices based on load.
% \item Introduced Puppet and Jenkins Job DSL to programmatically manage build server configuration.
% \item Introduced and ran weekly meetings to plan security improvements and respond to incidents.
% \item Created a signing server that provided code signatures for authenticated upgrades.
}
\end{itemize}
 }

\section{Education}
\cventry{2009 - 2013}{BS in Computer Science and Mathematics}{Carnegie Mellon
University}{3.8 QPA}{}{
\begin{itemize}
\item Interned at Amazon (Kindle Sales), Google (Social Search Ads), and Apple (OSX Performance).
\item Worked as teaching assistant for 3 classes, including 15-418 Parallel Computer Architecture. % and Programming.
\item Won DEFCON CTF in 2013 and 2014 as member of Plaid Parliament of Pwning.
\end{itemize}
}

\section{Extracurriculars}
\cventry{2012-2022}{Assistant Scoutmaster}{Boy Scouts of America}{}{}{}
\cventry{2008}{Eagle Scout}{Boy Scouts of America}{}{}{}

\end{document}
